---
title: 'R to C: The Comprehensive Guide'
output:
  pdf_document: default
  html_document: default
---


# Setup:

## Installation

Run the makefile as appropriate. Make sure that R.h and Rinternals.h are in your path. You can get these by installing the [R binary](https://www.r-project.org). However, the R IDE, [RStudio](https://rstudio.com/products/rstudio/download/#download), is an **extremely** helpful addition.

```{bash eval=FALSE}
# run me!
make interface
```

## Linking the library and running c code

#### 1) Start R in terminal using the command:

```{bash eval=FALSE}
sudo R
```

*note*: sudo permissions are important for using the pcap library in c.

#### 2) While in R, it requires us to link the library in R using:

```{r eval=FALSE}
dyn.load("interface.so")
```


#### 3) Test it out! Call a C function from R using `.Call("my_c_function", ...)`, where the elipses supply the parameters, if necessary. Try it using:

```{r eval=FALSE}
.Call("testThread")
```


#### 4) In order to use capture.c, we should follow these steps:

```{r eval=FALSE}
# This will startup capture.c, which will reroute standard out to /dev/null. This ensures that our terminal will only be printing output from R functions, and not the Rapid-fire chatter of packets.
.Call("startSession")

# Use this to end the session of capture.c, which will stop the thread running in the backround. A successful halt will return 0. Non-successful halts will return a non-zero number.
.Call("endSession")
```


## Running RShiny

#### 1) Install RShiny using either bash or R

```{bash eval=FALSE}
# bash
R -e "install.packages(\"shiny\", repos=\"http://cran.us.r-project.org\")"
```

```{r eval=FALSE}
# R
install.packages("shiny", repos = "http://cran.us.r-project.org")
```

#### 2) Run the Server!

```{bash eval=FALSE}
# bash
# Warning: dont run this inside the RMarkdown Document. It may hide the port number.
R -e "shiny::runApp('./Viewer')"
```

```{r eval=FALSE}
# R
shiny::runApp('./Viewer')
```

